Mozilla Data Science Project - 2019

### 2019-12-12 poc/EDA/EDA.Rmd
updating the EDA notebook

---
title: "Mozilla Data Science Project - 2019"
author: "Mariana de Oliveira Santos Silva"
date: "December 05, 2019"
output: 
  html_document:
    toc: true
    theme: united
    highlight: textmate
---

# Exploratory Data Analysis (EDA) {.tabset}

@@

## Setting-up

```{r message=FALSE, warning=FALSE}
## Loading the needed libraries

library(kableExtra)      # help you build common complex tables and manipulate table styles
library(tidyverse)       # for general data wrangling (includes readr and dplyr)
library(ggplot2)         # to draw statistical plots 
library(plotly)          # to construct interactive 3d plots
library(DataExplorer)    # automated data exploration
library(corrplot)        # to plot nice correlation matrix
library(caret)           # includes several functions to pre-process
library(scales)          # to determining breaks and labels for axes and legends
library(skimr)
library(funModeling) 
library(Hmisc)
```

@@

load("~/GitHub/ff-beta-release-matching/poc/EDA/data_milestone2_df_train_validate_20191021.RData")
```

@@

@@

To get introduced to our dataset:

```{r}
kable(introduce(df_train_f)) %>%
kable_styling(bootstrap_options = c("striped", "hover", "condensed"), full_width = F) %>%
scroll_box(width = "100%")
```

Let's have a look on the basic information of the dataset.

```{r, fig.width = 10, fig.height = 5}
plot_intro(df_train_f, ggtheme = theme_minimal())
```

Sanity check on the structure and show sample data for each variable.

```{r}
str(df_train_f)
```

When we get a new dataset to analyze, is important to know if there are missing values and the data type. The `df_status` function can help us by showing these numbers in relative and percentage values.

```{r}
kable(df_status(df_train_f)) %>%
kable_styling(bootstrap_options = c("striped", "hover", "condensed"), full_width = F) %>%
scroll_box(width = "100%")
```

@@

@@

`to-do`
<!-- Factor/categorical variables with a high number of different values (~30) tend to do overfitting if the categories have low cardinality. -->

## Step 2 : Analyzing Categorical Variables

```{r}
df_release <- df_train_f[which(df_train_f$label == 'release'), ]
df_beta <- df_train_f[which(df_train_f$label == 'beta'), ]

freq(df_train_f$label)
```

```{r, fig.width = 15, fig.height = 15}
## Frequency distribution of all discrete variables
plot_bar(df_train_f)
```

```{r, fig.width = 15, fig.height = 15}
## Frequency distribution for release dataframe
plot_bar(df_release)
```

```{r, fig.width = 15, fig.height = 15}
## Frequency distribution beta dataframe
plot_bar(df_beta)
```

### EDA on Coninuous Variables

```{r, fig.width = 15, fig.height = 15}
## View histogram of all continuous variables
plot_histogram(df_train_f)
```

```{r, fig.width = 15, fig.height = 15}
## View histogram of all continuous variables
plot_histogram(df_release)
```

```{r, fig.width = 15, fig.height = 15}
## View histogram of all continuous variables
plot_histogram(df_beta)
```

>>>>

---
title: "Mozilla Data Science Project - 2019"
author: "Mariana de Oliveira Santos Silva"
date: "December 05, 2019"
output: 
  html_document:
    toc: true
    toc_float: true
    highlight: tango
    df_print: kable
    code_folding: "hide"
    theme: "flatly"
---

# Exploratory Data Analysis (EDA)

@@

## Setting-up
```{r message=FALSE, warning=FALSE}
## Loading the needed libraries

library(kableExtra)      # help you build common complex tables and manipulate table styles
library(tidyverse)       # for general data wrangling (includes readr and dplyr)
library(ggplot2)         # to draw statistical plots 
library(plotly)          # to construct interactive 3d plots
library(DataExplorer)    # automated data exploration
library(corrplot)        # to plot nice correlation matrix
library(caret)           # includes several functions to pre-process
library(scales)          # to determining breaks and labels for axes and legends
library(skimr)
library(funModeling) 
library(Hmisc)
library(grid)
library(hrbrthemes)
library(tidyr)
library(viridis)
library(ggpubr)
library(ggthemes)
library(GGally)
library(nortest)
```

@@

load("~/GitHub/ff-beta-release-matching/poc/EDA/data_milestone2_df_train_validate_20191025.RData")
```

## Training

@@

## Validation

kable(head(df_validate_f)) %>%
kable_styling(bootstrap_options = c("striped", "hover", "condensed"), full_width = F) %>%
scroll_box(width = "100%")
```

@@

### Training

To get introduced to our training dataset, let's have a look on the basic information of the dataset.

```{r echo=FALSE}
kable(introduce(df_train_f)) %>%
kable_styling(bootstrap_options = c("striped", "hover", "condensed"), full_width = F) %>%
scroll_box(width = "100%")
```

```{r echo=FALSE, fig.height=10, fig.width=10}
plot_intro(df_train_f, ggtheme = theme_minimal())
```

### Validation

To get introduced to our validation dataset, let's have a look on the basic information of the dataset.

```{r echo=FALSE}
kable(introduce(df_validate_f)) %>%
kable_styling(bootstrap_options = c("striped", "hover", "condensed"), full_width = F) %>%
scroll_box(width = "100%")
```

```{r echo=FALSE, fig.height=10, fig.width=10}
plot_intro(df_validate_f, ggtheme = theme_minimal())
```

### Observations

* Most of the dataset is composed of continuous variables
* No NAs values (were handled in preprocessing)

## Data Structure

### Training

Let's use `glimpse` function to display a vertical preview of the training dataset. So we can easily preview data type and sample data.

```{r}
glimpse(df_train_f)
```

If we want to get some metrics about data types, zeros, infinite numbers, and missing values, we can use the `df_status` function.

```{r}
kable(df_status(df_train_f, FALSE)) %>%
kable_styling(bootstrap_options = c("striped", "hover", "condensed"), full_width = F) %>%
scroll_box(width = "100%")
```

@@

### Validation

Let's use `glimpse` function to display a vertical preview of the validation dataset. So we can easily preview data type and sample data.

```{r}
glimpse(df_validate_f)
```

If we want to get some metrics about data types, zeros, infinite numbers, and missing values, we can use the `df_status` function.

```{r}
kable(df_status(df_train_f, FALSE)) %>%
kable_styling(bootstrap_options = c("striped", "hover", "condensed"), full_width = F) %>%
scroll_box(width = "100%")
```

### Observations

@@

Factor/categorical variables with a high number of different values (~30) tend to do overfitting if the categories have low cardinality.

## Step 2 : Beta vs Release

### Training

```{r, fig.width = 7.5}
df_release <- df_train_f[which(df_train_f$label == 'release'), ]
df_beta <- df_train_f[which(df_train_f$label == 'beta'), ]

f <- freq(df_train_f$label)
```

```{r}
summary(df_release)
```

```{r}
summary(df_beta)
```

### Validation

```{r, fig.width = 7.5}
df_v_release <- df_validate_f[which(df_validate_f$label == 'release'), ]
df_v_beta <- df_validate_f[which(df_validate_f$label == 'beta'), ]

f <- freq(df_validate_f$label)
```

```{r}
summary(df_v_release)
```

```{r}
summary(df_v_beta)
```

## Step 3 - Analyzing Discrete Variables

### Training

```{r, fig.height=15, fig.width=15, message=FALSE, warning=FALSE}
## Frequency distribution release dataframe
plot_bar(df_release, ggtheme = theme_minimal(base_size = 15))
```

```{r, fig.height=15, fig.width=15, message=FALSE, warning=FALSE}
## Frequency distribution beta dataframe
plot_bar(df_beta, ggtheme = theme_minimal(base_size = 15))
```

### Validation

```{r, fig.height=15, fig.width=15, message=FALSE, warning=FALSE}
## Frequency distribution release dataframe
plot_bar(df_v_release, ggtheme = theme_minimal(base_size = 15))
```

```{r, fig.height=15, fig.width=15, message=FALSE, warning=FALSE}
## Frequency distribution beta dataframe
plot_bar(df_v_beta, ggtheme = theme_minimal(base_size = 15))
```

## Step 4 - Analyzing Continuos Variables

### Training

```{r, fig.width = 15, fig.height = 15}
## View histogram of release dataset
plot_histogram(df_release, ggtheme = theme_minimal(base_size = 15))
```

```{r, fig.width = 15, fig.height = 15}
## View histogram of beta dataset
plot_histogram(df_beta, ggtheme = theme_minimal(base_size = 15))
```

### Validation

```{r, fig.width = 15, fig.height = 15}
## View histogram of release dataset
plot_histogram(df_release, ggtheme = theme_minimal(base_size = 15))
```

```{r, fig.width = 15, fig.height = 15}
## View histogram of beta dataset
plot_histogram(df_beta, ggtheme = theme_minimal(base_size = 15))
```

### Observations

* My first impression is that **user engagement** metrics might be a good path to follow

### Ploting Density Curves

```{r include=FALSE}
require(cowplot)
```

```{r, fig.width = 20, fig.height = 5, message=FALSE, warning=FALSE}
## Training
t <- ggplot(data=df_train_f, aes(x=uri_count, group=label, fill=label)) +
    geom_density(adjust=1.5, alpha=0.6) + xlim(0, 1000) +
    scale_fill_viridis(discrete=TRUE) +
    scale_color_viridis(discrete=TRUE) +
    labs(x="URI Count", y = "Density") +
    theme_ipsum()

## Validation
v <- ggplot(data=df_validate_f, aes(x=uri_count, group=label, fill=label)) +
    geom_density(adjust=1.5, alpha=0.6) + xlim(0, 1000) +
    scale_fill_viridis(discrete=TRUE) +
    scale_color_viridis(discrete=TRUE) +
    labs(x="URI Count", y = "Density") +
    theme_ipsum()

plot_grid(t, v, ncol=2, labels = c("Train", "Validate")) ## Set up a 2 x 2 plotting space
```

```{r, fig.width = 20, fig.height = 5, message=FALSE, warning=FALSE}
## Training
t <- ggplot(data=df_train_f, aes(x=active_hours, group=label, fill=label)) +
    geom_density(adjust=1.5, alpha=0.6) +
    scale_fill_viridis(discrete=TRUE) +
    scale_color_viridis(discrete=TRUE) +
    labs(x="Active Hours", y = "Density") +
    theme_ipsum()

## Validation
v <- ggplot(data=df_validate_f, aes(x=active_hours, group=label, fill=label)) +
    geom_density(adjust=1.5, alpha=0.6) +
    scale_fill_viridis(discrete=TRUE) +
    scale_color_viridis(discrete=TRUE) +
    labs(x="Active Hours", y = "Density") +
    theme_ipsum()

plot_grid(t, v, ncol=2, labels = c("Train", "Validate")) ## Set up a 2 x 2 plotting space
```

```{r, fig.width = 20, fig.height = 5, message=FALSE, warning=FALSE}
## Training
t <- ggplot(data=df_train_f, aes(x=num_pages, group=label, fill=label)) +
    geom_density(adjust=1.5, alpha=0.6) + xlim(0, 50000) +
    scale_fill_viridis(discrete=TRUE) +
    scale_color_viridis(discrete=TRUE) +
    labs(x="Num Pages", y = "Density") +
    theme_ipsum()

## Validation
v <- ggplot(data=df_validate_f, aes(x=num_pages, group=label, fill=label)) +
    geom_density(adjust=1.5, alpha=0.6) + xlim(0, 50000) +
    scale_fill_viridis(discrete=TRUE) +
    scale_color_viridis(discrete=TRUE) +
    labs(x="Num Pages", y = "Density") +
    theme_ipsum()

plot_grid(t, v, ncol=2, labels = c("Train", "Validate")) ## Set up a 2 x 2 plotting space
```

```{r, fig.width = 20, fig.height = 5, message=FALSE, warning=FALSE}
## Training
t <- ggplot(data=df_train_f, aes(x=session_length, group=label, fill=label)) +
    geom_density(adjust=1.5, alpha=0.6) + xlim(0, 75) +
    scale_fill_viridis(discrete=TRUE) +
    scale_color_viridis(discrete=TRUE) +
    labs(x="Session Length", y = "Density") +
    theme_ipsum()

## Validation
v <- ggplot(data=df_validate_f, aes(x=session_length, group=label, fill=label)) +
    geom_density(adjust=1.5, alpha=0.6) + xlim(0, 75) +
    scale_fill_viridis(discrete=TRUE) +
    scale_color_viridis(discrete=TRUE) +
    labs(x="Session Length", y = "Density") +
    theme_ipsum()

plot_grid(t, v, ncol=2, labels = c("Train", "Validate")) ## Set up a 2 x 2 plotting space
```

# User Engagement Continuous Metrics

This section will focus only on user engagement continuous metrics. So, we are going to analyze the following metrics:

* `num_active_days`
* `active_hours`
* `active_hours_max`
* `uri_count`
* `uri_count_max`
* `session_length`
* `session_length_max`
* `search_count`
* `search_count_max`
* `num_bookmarks`
* `num_pages`
* `num_pages_max`
* `num_addons`
* `daily_unique_domains`
* `daily_unique_domains_max`
* `daily_max_tabs`
* `daily_max_tabs_max`
* `daily_tabs_opened`
* `daily_tabs_opened_max`
* `daily_num_sessions_started`
* `daily_num_sessions_started_max`
* `startup_ms`
* `install_year`
* `profile_age`
* `timezone_offset`
* `memory_mb`
* `cpu_cores`
* `cpu_speed_mhz`
* `cpu_l2_cache_kb`

```{r include=FALSE}
user_eng <- c("num_active_days","active_hours","active_hours_max","uri_count","uri_count_max","session_length","session_length_max","search_count","search_count_max","num_bookmarks","num_pages","num_pages_max","num_addons","daily_unique_domains","daily_unique_domains_max","daily_max_tabs","daily_max_tabs_max","daily_tabs_opened","daily_tabs_opened_max","daily_num_sessions_started","daily_num_sessions_started_max","startup_ms","install_year","profile_age","timezone_offset","memory_mb","cpu_cores","cpu_speed_mhz","cpu_l2_cache_kb")
```

```{r include=FALSE}
df_beta_ue <- df_beta %>% select(user_eng)
df_release_ue <- df_release %>% select(user_eng)
df_train_ue <- df_train_f %>% select(c(user_eng, "label"))

df_beta_v_ue <- df_v_beta %>% select(user_eng)
df_release_v_ue <- df_v_release %>% select(user_eng)
df_validate_ue <- df_validate_f %>% select(c(user_eng, "label"))
```

```{r include=FALSE}
text_tbl <- data.frame(
beta_num_active_days = c(summary(df_beta_ue$num_active_days)), release_num_active_days = c(summary(df_release_ue$num_active_days)), 
beta_active_hours = c(summary(df_beta_ue$active_hours)), release_active_hours = c(summary(df_release_ue$active_hours)), 
beta_active_hours_max = c(summary(df_beta_ue$active_hours_max)), release_active_hours_max = c(summary(df_release_ue$active_hours_max)), 
beta_uri_count = c(summary(df_beta_ue$uri_count)), release_uri_count = c(summary(df_release_ue$uri_count)), 
beta_uri_count_max = c(summary(df_beta_ue$uri_count_max)), release_uri_count_max = c(summary(df_release_ue$uri_count_max)), 
beta_session_length = c(summary(df_beta_ue$session_length)), release_session_length = c(summary(df_release_ue$session_length)), 
beta_session_length_max = c(summary(df_beta_ue$session_length_max)), release_session_length_max = c(summary(df_release_ue$session_length_max)), 
beta_search_count = c(summary(df_beta_ue$search_count)), release_search_count = c(summary(df_release_ue$search_count)), 
beta_search_count_max = c(summary(df_beta_ue$search_count_max)), release_search_count_max = c(summary(df_release_ue$search_count_max)), 
beta_num_bookmarks = c(summary(df_beta_ue$num_bookmarks)), release_num_bookmarks = c(summary(df_release_ue$num_bookmarks)), 
beta_num_pages = c(summary(df_beta_ue$num_pages)), release_num_pages = c(summary(df_release_ue$num_pages)), 
beta_num_pages_max = c(summary(df_beta_ue$num_pages_max)), release_num_pages_max = c(summary(df_release_ue$num_pages_max)), 
beta_daily_unique_domains = c(summary(df_beta_ue$daily_unique_domains)), release_daily_unique_domains = c(summary(df_release_ue$daily_unique_domains)), 
beta_daily_max_tabs = c(summary(df_beta_ue$daily_max_tabs)), release_daily_max_tabs = c(summary(df_release_ue$daily_max_tabs)), 
beta_daily_tabs_opened = c(summary(df_beta_ue$daily_tabs_opened)), release_daily_tabs_opened = c(summary(df_release_ue$daily_tabs_opened)), 
beta_daily_num_sessions_started = c(summary(df_beta_ue$daily_num_sessions_started)), release_daily_num_sessions_started = c(summary(df_release_ue$daily_num_sessions_started)), 
beta_daily_unique_domains_max = c(summary(df_beta_ue$daily_unique_domains_max)), release_daily_unique_domains_max = c(summary(df_release_ue$daily_unique_domains_max)), 
beta_daily_max_tabs_max = c(summary(df_beta_ue$daily_max_tabs_max)), release_daily_max_tabs_max = c(summary(df_release_ue$daily_max_tabs_max)), 
beta_daily_tabs_opened_max = c(summary(df_beta_ue$daily_tabs_opened_max)), release_daily_tabs_opened_max = c(summary(df_release_ue$daily_tabs_opened_max)), 
beta_daily_num_sessions_started_max = c(summary(df_beta_ue$daily_num_sessions_started_max)), release_daily_num_sessions_started_max = c(summary(df_release_ue$daily_num_sessions_started_max)), 
beta_startup_ms = c(summary(df_beta_ue$startup_ms)), release_startup_ms = c(summary(df_release_ue$startup_ms)), 
beta_install_year = c(summary(df_beta_ue$install_year)), release_install_year = c(summary(df_release_ue$install_year)), 
beta_profile_age = c(summary(df_beta_ue$profile_age)), release_profile_age = c(summary(df_release_ue$profile_age)), 
beta_timezone_offset = c(summary(df_beta_ue$timezone_offset)), release_timezone_offset = c(summary(df_release_ue$timezone_offset)), 
beta_memory_mb = c(summary(df_beta_ue$memory_mb)), release_memory_mb = c(summary(df_release_ue$memory_mb)), 
beta_cpu_cores = c(summary(df_beta_ue$cpu_cores)), release_cpu_cores = c(summary(df_release_ue$cpu_cores)), 
beta_cpu_speed_mhz = c(summary(df_beta_ue$cpu_speed_mhz)), release_cpu_speed_mhz = c(summary(df_release_ue$cpu_speed_mhz)), 
beta_cpu_l2_cache_kb = c(summary(df_beta_ue$cpu_l2_cache_kb)), release_cpu_l2_cache_kb = c(summary(df_release_ue$cpu_l2_cache_kb))
)
```

```{r include=FALSE}
text_tbl_v <- data.frame(
beta_num_active_days = c(summary(df_beta_v_ue$num_active_days)), release_num_active_days = c(summary(df_release_v_ue$num_active_days)), 
beta_active_hours = c(summary(df_beta_v_ue$active_hours)), release_active_hours = c(summary(df_release_v_ue$active_hours)), 
beta_active_hours_max = c(summary(df_beta_v_ue$active_hours_max)), release_active_hours_max = c(summary(df_release_v_ue$active_hours_max)), 
beta_uri_count = c(summary(df_beta_v_ue$uri_count)), release_uri_count = c(summary(df_release_v_ue$uri_count)), 
beta_uri_count_max = c(summary(df_beta_v_ue$uri_count_max)), release_uri_count_max = c(summary(df_release_v_ue$uri_count_max)), 
beta_session_length = c(summary(df_beta_v_ue$session_length)), release_session_length = c(summary(df_release_v_ue$session_length)), 
beta_session_length_max = c(summary(df_beta_v_ue$session_length_max)), release_session_length_max = c(summary(df_release_v_ue$session_length_max)), 
beta_search_count = c(summary(df_beta_v_ue$search_count)), release_search_count = c(summary(df_release_v_ue$search_count)), 
beta_search_count_max = c(summary(df_beta_v_ue$search_count_max)), release_search_count_max = c(summary(df_release_v_ue$search_count_max)), 
beta_num_bookmarks = c(summary(df_beta_v_ue$num_bookmarks)), release_num_bookmarks = c(summary(df_release_v_ue$num_bookmarks)), 
beta_num_pages = c(summary(df_beta_v_ue$num_pages)), release_num_pages = c(summary(df_release_v_ue$num_pages)), 
beta_num_pages_max = c(summary(df_beta_v_ue$num_pages_max)), release_num_pages_max = c(summary(df_release_v_ue$num_pages_max)), 
beta_daily_unique_domains = c(summary(df_beta_v_ue$daily_unique_domains)), release_daily_unique_domains = c(summary(df_release_v_ue$daily_unique_domains)), 
beta_daily_max_tabs = c(summary(df_beta_v_ue$daily_max_tabs)), release_daily_max_tabs = c(summary(df_release_v_ue$daily_max_tabs)), 
beta_daily_tabs_opened = c(summary(df_beta_v_ue$daily_tabs_opened)), release_daily_tabs_opened = c(summary(df_release_v_ue$daily_tabs_opened)), 
beta_daily_num_sessions_started = c(summary(df_beta_v_ue$daily_num_sessions_started)), release_daily_num_sessions_started = c(summary(df_release_v_ue$daily_num_sessions_started)), 
beta_daily_unique_domains_max = c(summary(df_beta_v_ue$daily_unique_domains_max)), release_daily_unique_domains_max = c(summary(df_release_v_ue$daily_unique_domains_max)), 
beta_daily_max_tabs_max = c(summary(df_beta_v_ue$daily_max_tabs_max)), release_daily_max_tabs_max = c(summary(df_release_v_ue$daily_max_tabs_max)), 
beta_daily_tabs_opened_max = c(summary(df_beta_v_ue$daily_tabs_opened_max)), release_daily_tabs_opened_max = c(summary(df_release_v_ue$daily_tabs_opened_max)), 
beta_daily_num_sessions_started_max = c(summary(df_beta_v_ue$daily_num_sessions_started_max)), release_daily_num_sessions_started_max = c(summary(df_release_v_ue$daily_num_sessions_started_max)), 
beta_startup_ms = c(summary(df_beta_v_ue$startup_ms)), release_startup_ms = c(summary(df_release_v_ue$startup_ms)), 
beta_install_year = c(summary(df_beta_v_ue$install_year)), release_install_year = c(summary(df_release_v_ue$install_year)), 
beta_profile_age = c(summary(df_beta_v_ue$profile_age)), release_profile_age = c(summary(df_release_v_ue$profile_age)), 
beta_timezone_offset = c(summary(df_beta_v_ue$timezone_offset)), release_timezone_offset = c(summary(df_release_v_ue$timezone_offset)), 
beta_memory_mb = c(summary(df_beta_v_ue$memory_mb)), release_memory_mb = c(summary(df_release_v_ue$memory_mb)), 
beta_cpu_cores = c(summary(df_beta_v_ue$cpu_cores)), release_cpu_cores = c(summary(df_release_v_ue$cpu_cores)), 
beta_cpu_speed_mhz = c(summary(df_beta_v_ue$cpu_speed_mhz)), release_cpu_speed_mhz = c(summary(df_release_v_ue$cpu_speed_mhz)), 
beta_cpu_l2_cache_kb = c(summary(df_beta_v_ue$cpu_l2_cache_kb)), release_cpu_l2_cache_kb = c(summary(df_release_v_ue$cpu_l2_cache_kb))
)
```

## Training

```{r}
kable(text_tbl) %>%
kable_styling(bootstrap_options = c("striped", "hover", "condensed"), full_width = F) %>%
scroll_box(width = "100%")
```

## Validation

```{r}
kable(text_tbl_v) %>%
kable_styling(bootstrap_options = c("striped", "hover", "condensed"), full_width = F) %>%
scroll_box(width = "100%")
```

## Comparing Two Continuous Distributions

### Training

The QQ plot can be used to compare two continuous distributions.

```{r fig.height=8, fig.width=8, message=FALSE, warning=FALSE}
par(mfrow = c(2, 2))  ## Set up a 2 x 2 plotting space

## QQ plot in R to compare two data samples
for (i in user_eng) {
  x <- df_beta_ue[,i]
  y <- df_release_ue[,i]

  rg <- range(x, y, na.rm=T)

  test <- ks.test(x, y)$statistic
  pvalue <- ks.test(x, y)$p.value

  test <- paste("KS Test = ", round(test, 3))
  pvalue <- paste("P-value = ", round(pvalue, 3))

  qqplot(x, y, main=i, xlim=rg, ylim=rg, xlab = "Beta", ylab = "Release", pch = 1)
  # mtext(test, side=3)
  text(min(x), max(x), paste(pvalue, "\n", test), adj=c(0,1))
  abline(0,1, col="red")  
}
```

```{r message=FALSE, warning=FALSE, out.width=c('50%', '50%')}
for (i in user_eng) {
  x <- df_beta_ue[,i]
  y <- df_release_ue[,i]

  print(i)
  # print(ad.test(x))
  # print(ad.test(y))
  print(ks.test(x, y))
}
```

### Validation

The QQ plot can be used to compare two continuous distributions.

```{r fig.height=8, fig.width=8, message=FALSE, warning=FALSE}
par(mfrow = c(2, 2))  ## Set up a 2 x 2 plotting space

## QQ plot in R to compare two data samples
for (i in user_eng) {
  x <- df_beta_v_ue[,i]
  y <- df_release_v_ue[,i]

  rg <- range(x, y, na.rm=T)

  test <- ks.test(x, y)$statistic
  pvalue <- ks.test(x, y)$p.value

  test <- paste("KS Test = ", round(test, 3))
  pvalue <- paste("P-value = ", round(pvalue, 3))

  qqplot(x, y, main=i, xlim=rg, ylim=rg, xlab = "Beta", ylab = "Release", pch = 1)
  # mtext(test, side=3)
  text(min(x), max(x), paste(pvalue, "\n", test), adj=c(0,1))
  abline(0,1, col="red")  
}
```

```{r message=FALSE, warning=FALSE, out.width=c('50%', '50%')}
for (i in user_eng) {
  x <- df_beta_v_ue[,i]
  y <- df_release_v_ue[,i]

  print(i)
  # print(ad.test(x))
  # print(ad.test(y))
  print(ks.test(x, y))
}
```

### Observations

* Analyzing only the plots, in general, the distributions are very similar to each other
* Mainly the metrics related to **active hours** and **number of active days**, **search count**, **number of pages**, **daily unique domains** and **daily number of sessions started**
* Comparing only the training and validation plots, we can notice that the variables that presented a more different behavior were: `num_active_days`, `uri_count_max` and `num_addons`
* When I performed the KS (kolmogorov-Smirnov) test, the null hypothesis that both samples come from the same distribution was rejected for all the comparisons. *Am I doing something wrong?*

# User Engagement Discrete Metrics

This section will focus only on user engagement continuous metrics. So, we are going to analyze the following metrics:

* `default_search_engine`
* `is_default_browser`
* `profile_age_cat`
* `distro_id_norm`
* `memory_cat`
* `cpu_speed_cat`
* `cpu_cores_cat`
* `cpu_l2_cache_kb_cat`
* `cpu_vendor`
* `os_version`
* `is_wow64`
* `fxa_configured`
* `sync_configured`
* `locale`
* `country`
* `timezone_cat`
* `label`
* `normalized_channel`
* `is_release`

```{r include=FALSE}
user_eng_dis <- c("default_search_engine","is_default_browser","profile_age_cat","distro_id_norm","memory_cat","cpu_speed_cat","cpu_cores_cat","cpu_l2_cache_kb_cat","cpu_vendor","os_version","is_wow64","fxa_configured","sync_configured","locale","country","timezone_cat","label","normalized_channel","is_release")
```

```{r include=FALSE}
df_beta_ue_dis <- df_beta %>% select(user_eng_dis)
df_release_ue_dis <- df_release %>% select(user_eng_dis)
df_train_ue_dis <- df_train_f %>% select(c(user_eng_dis, "label"))

df_beta_v_ue_dis <- df_v_beta %>% select(user_eng_dis)
df_release_v_ue_dis <- df_v_release %>% select(user_eng_dis)
df_validate_ue_dis <- df_validate_f %>% select(c(user_eng_dis, "label"))
```

## Comparing Two Discrete Distributions

### Training

```{r fig.height=8, fig.width=8, message=FALSE, warning=FALSE}
par(mfrow = c(2, 2))  ## Set up a 2 x 2 plotting space

## QQ plot in R to compare two data samples
for (i in user_eng_dis) {
  x <- df_beta_ue_dis[,i]
  y <- df_release_ue_dis[,i]

  rel_beta <- table(x)/nrow(df_beta_ue_dis) #divide the frequency counts by the total
  beta_bar <- barplot(rel_beta,
        main = "Beta", #Give your chart a title
        ylim=c(0,1), border=F, col = "navy",
        xlab = i, #Label the x axis
        ylab = "Relative Frequency" #Label the y axis
  ) 
  # Add the text 
  text(beta_bar, rel_beta+0.025, paste(round(rel_beta*100), "%", sep="") ,cex=1)

  rel_release <- table(y)/nrow(df_release_ue_dis) #divide the frequency counts by the total
  release_bar <- barplot(rel_release,
        main = "Release", #Give your chart a title
        ylim=c(0,1), border=F, col = "navy",
        xlab = i, #Label the x axis
        ylab = "Relative Frequency" #Label the y axis
  )

  # Add the text 
  text(release_bar, rel_release+0.025, paste(round(rel_release*100), "%", sep="") ,cex=1) 
}
```

### Validation

```{r fig.height=8, fig.width=8, message=FALSE, warning=FALSE}
par(mfrow = c(2, 2))  ## Set up a 2 x 2 plotting space

## QQ plot in R to compare two data samples
for (i in user_eng_dis) {
  x <- df_beta_v_ue_dis[,i]
  y <- df_release_v_ue_dis[,i]

  rel_beta <- table(x)/nrow(df_beta_v_ue_dis) #divide the frequency counts by the total
  beta_bar <- barplot(rel_beta,
        main = "Beta", #Give your chart a title
        ylim=c(0,1), border=F, col = "navy",
        xlab = i, #Label the x axis
        ylab = "Relative Frequency" #Label the y axis
  ) 
  # Add the text 
  text(beta_bar, rel_beta+0.025, paste(round(rel_beta*100), "%", sep="") ,cex=1)

  rel_release <- table(y)/nrow(df_release_v_ue_dis) #divide the frequency counts by the total
  release_bar <- barplot(rel_release,
        main = "Release", #Give your chart a title
        ylim=c(0,1), border=F, col = "navy",
        xlab = i, #Label the x axis
        ylab = "Relative Frequency" #Label the y axis
  )

  # Add the text 
  text(release_bar, rel_release+0.025, paste(round(rel_release*100), "%", sep="") ,cex=1) 
}
```

### Observations

* Analyzing only the plots, in general, the distributions are very similar to each other
